Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-02 ms.tex
a few short notes about the topological defects and how they may relate to flat fields

The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
The surface morphology of HgCdTe shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes \citep{chang2008surfaceMorphologyHgCdTe}.
HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
In this perspective, the projected bond angles form angles of 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.

>>>>

The angles of the crosshatch patterns are likely determined by the crystal pattern of HgCdTe.
HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
In this perspective, the projected bond angles form angles of 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.

HgCdTe detectors are manufactured using Molecular Beam Epitaxy upon a substrate, a process which results in topological defects with peak to valley amplitudes of 5-20 nm in height variations.
The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes \citep{chang2008surfaceMorphologyHgCdTe}.
The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$, very close to the observed crosshatch angles.
These surface topological variations with crosshatch patterns are likely related to the observed patterns in the flat fields, which are caused by quantum efficiency variations.
We deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
